\thetitle

### 2013-04-13 tfpie/tfpie.tex
formatting

;; A World (new world% Number)
(define-class world%
  (fields n)
  ;; on-tick : -> World
  (define (on-tick)
    (new world% (add1 (this . n))))
  ;; to-draw : -> Image
  (define (on-tick) 
    (circle (this . n) "solid" "red"))
  ;; on-key : KeyEvent -> World
  (define (on-key k) (new world% 10)))

>>>>

;; A World is a (new world% Number)
(define-class world%
  (fields n)

  ;; on-tick : -> World
  (define (on-tick)
    (new world% (add1 (this . n))))

  ;; to-draw : -> Image
  (define (on-tick) 
    (circle (this . n) "solid" "red"))

  ;; on-key : KeyEvent -> World
  (define (on-key k) (new world% 10)))
